\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-15 submission/manuscript.Rmd
format comments

### Attractiveness and Beauty (males -positive linear; females -quadratic(u-shape); judgement confidence positive quadratic relationship for females only in the real condition)

@@

### trustworthiness

@@

### familiarity (confidence judgement; positive linear -real; quadratic -fake)
Contrary to our hypothesis, familiarity was not found to have any significant effects on simulation monitoring decisions.

### inter-indiv correlates (HH- negative with confidence in real; positive with acclaim-seeking and grandiose; Acc-seeking - positive with confidence in fake)

### AI attitudes (enthusiam - positive with confidence in both real and fake judgements)

### Re-exposure Delay

>>>>

<!-- Attractiveness and Beauty (males -positive linear; females -quadratic(u-shape); judgement confidence positive quadratic relationship for females only in the real condition) -->

@@

<!-- trustworthiness -->

@@

<!-- familiarity (confidence judgement; positive linear -real; quadratic -fake) -->
Contrary to our hypothesis, familiarity was not found to have any significant effects on simulation monitoring decisions.

<!-- inter-indiv correlates (HH- negative with confidence in real; positive with acclaim-seeking and grandiose; Acc-seeking - positive with confidence in fake) -->

<!-- AI attitudes (enthusiam - positive with confidence in both real and fake judgements) -->

<!-- Re-exposure Delay -->
